The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-08 main.tex

The \package{astropy.io} subpackage provides support for reading and writing
data to a variety of ASCII and binary file formats, such as a wide range of
ASCII data table formats, FITS, and VOTable.
It also provides a unified interface for reading and writing data with these
different formats using the \package{astropy.table} subpackage.
For many common cases, this simplifies the process of file input and output (I/O) and
reduces the need to master the separate details of all the I/O packages within
\astropypkg. The file interface allows transparent compression of
the \texttt{gzip}, \texttt{bzip2} and \texttt{lzma} (\texttt{.xz})
formats; for the latter two if the Python installation was compiled
with support the respective libraries.

>>>>

The \package{astropy.io} subpackage provides support for reading and writing
data to a variety of ASCII and binary file formats, such as a wide range of
ASCII data table formats, FITS, HDF5, and VOTable.
It also provides a unified interface for reading and writing data with these
different formats using the \package{astropy.table} subpackage.
For many common cases, this simplifies the process of file input and output (I/O) and
reduces the need to master the separate details of all the I/O packages within
\astropypkg. The file interface allows transparent compression of
the \texttt{gzip}, \texttt{bzip2} and \texttt{lzma} (\texttt{.xz})
formats; for the latter two if the Python installation was compiled
with support the respective libraries.
